Through the Eyes of the Teacher - Multimodal Exploration of Expertise Differences in the Perception of Classroom Disruptions in a Laboratory Study

### 2025-01-28 02_paper/02_study/02_expertise_paper/expertise_2025_01_23_MK.Rmd
x paper

# Gaze Allocation Across Areas of Interest 
```{r nof__dur_percent, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#### Percentage of fixations on each AOI, relative to the total number of fixations during the entire "Lesson" 
# Step 1: Define AOI categories
aoi_columns <- list(
  "AOI_Students" = c(
    "Number_of_fixations.Anna",
    "Number_of_fixations.Bianca",
    "Number_of_fixations.Carl(a)"
  ),
  "AOI_Disruptive_Person" = c("Number_of_fixations.Disruptive_Person"),
  "AOI_Teacher_Material" = c(
    "Number_of_fixations.Board_Screen",
    "Number_of_fixations.Material_Teacher"
  ),
  "AOI_Student_Desk" = c(
    "Number_of_fixations.Nametag_Anna",
    "Number_of_fixations.Nametag_Bianca",
    "Number_of_fixations.Nametag_Carl(a)",
    "Number_of_fixations.Material_Students"
  ),
  "AOI_Classroom_Others" = c("Number_of_fixations.Classroom_Others")
)

@@

# Step 3: Calculate total fixations per participant, excluding "Disruptive Person"
# Extract relevant column names excluding "Disruptive Person"
relevant_columns <- unlist(aoi_columns[c("AOI_Students", "AOI_Teacher_Material", "AOI_Student_Desk", "AOI_Classroom_Others")])

@@

# Step 5: Summarize fixation percentages by Group and arrange in descending order
grouped_aoi_percentages <- aoi_percentages %>%
  group_by(Group) %>%
  summarise(
    Mean_AOI_Students_pct = round(mean(AOI_Students_pct, na.rm = TRUE), 2),
    Mean_AOI_Disruptive_Person_pct = round(mean(AOI_Disruptive_Person_pct, na.rm = TRUE), 2),
    Mean_AOI_Teacher_Material_pct = round(mean(AOI_Teacher_Material_pct, na.rm = TRUE), 2),
    Mean_AOI_Student_Desk_pct = round(mean(AOI_Student_Desk_pct, na.rm = TRUE), 2),
    Mean_AOI_Classroom_Others_pct = round(mean(AOI_Classroom_Others_pct, na.rm = TRUE), 2)
  ) %>%
  pivot_longer(cols = starts_with("Mean_AOI"), names_to = "AOI", values_to = "Fixation_Percentage") %>%
  mutate(AOI = recode(AOI,
                      "Mean_AOI_Students_pct" = "Students",
                      "Mean_AOI_Disruptive_Person_pct" = "Disruptive Person",
                      "Mean_AOI_Teacher_Material_pct" = "Teacher Material",
                      "Mean_AOI_Student_Desk_pct" = "Student Desk",
                      "Mean_AOI_Classroom_Others_pct" = "Classroom/Others")) %>%
  arrange(Group, desc(Fixation_Percentage))

# Step 6: Restructure data for grouping and calculate 95% CI
grouped_aoi_percentages_ci <- aoi_percentages %>%
  pivot_longer(
    cols = starts_with("AOI"),
    names_to = "AOI",
    values_to = "Percentage"
  ) %>%
  mutate(AOI = recode(
    AOI,
    "AOI_Students_pct" = "Students",
    "AOI_Disruptive_Person_pct" = "Disruptive Person",
    "AOI_Teacher_Material_pct" = "Teacher Material",
    "AOI_Student_Desk_pct" = "Student Desk",
    "AOI_Classroom_Others_pct" = "Classroom/Others"
  )) %>%
  group_by(Group, AOI) %>%
  summarise(
    Mean_Percentage = mean(Percentage, na.rm = TRUE),
    CI_Lower = Mean_Percentage - qt(0.975, df = n() - 1) * sd(Percentage, na.rm = TRUE) / sqrt(n()),
    CI_Upper = Mean_Percentage + qt(0.975, df = n() - 1) * sd(Percentage, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  )

@@

# Clean up AOI names for readability in the final table
aoi_name_mapping <- c(
  "AOI_Students" = "Students",
  "AOI_Disruptive_Person" = "Disruptive Person",
  "AOI_Teacher_Material" = "Teacher Material",
  "AOI_Student_Desk" = "Student Desk",
  "AOI_Classroom_Others" = "Classroom/Others"
)
results_number$AOI <- aoi_name_mapping[results_number$AOI]

@@

#### Percentage of fixation durations on each AOI, relative to the total duration of fixations during the entire "Lesson" 
# Step 1: Define AOI categories with correct column names for fixation duration
aoi_columns <- list(
  "AOI_Students" = c(
    "Total_duration_of_fixations.Anna",
    "Total_duration_of_fixations.Bianca",
    "Total_duration_of_fixations.Carl(a)"
  ),
  "AOI_Disruptive_Person" = c("Total_duration_of_fixations.Disruptive_Person"),
  "AOI_Teacher_Material" = c(
    "Total_duration_of_fixations.Board_Screen",
    "Total_duration_of_fixations.Material_Teacher"
  ),
  "AOI_Student_Desk" = c(
    "Total_duration_of_fixations.Nametag_Anna",
    "Total_duration_of_fixations.Nametag_Bianca",
    "Total_duration_of_fixations.Nametag_Carl(a)",
    "Total_duration_of_fixations.Material_Students"
  ),
  "AOI_Classroom_Others" = c("Total_duration_of_fixations.Classroom_Others")
)

# Step 3: Calculate total fixation duration per participant, excluding "Disruptive Person"
relevant_columns <- unlist(aoi_columns[c("AOI_Students", "AOI_Teacher_Material", "AOI_Student_Desk", "AOI_Classroom_Others")])

# Step 5: Summarize fixation duration percentages by Group and arrange in descending order
grouped_aoi_durations_percentages <- aoi_durations_percentages %>%
  group_by(Group) %>%
  summarise(
    Mean_AOI_Students_pct = round(mean(AOI_Students_pct, na.rm = TRUE), 2),
    Mean_AOI_Disruptive_Person_pct = round(mean(AOI_Disruptive_Person_pct, na.rm = TRUE), 2),
    Mean_AOI_Teacher_Material_pct = round(mean(AOI_Teacher_Material_pct, na.rm = TRUE), 2),
    Mean_AOI_Student_Desk_pct = round(mean(AOI_Student_Desk_pct, na.rm = TRUE), 2),
    Mean_AOI_Classroom_Others_pct = round(mean(AOI_Classroom_Others_pct, na.rm = TRUE), 2)
  ) %>%
  pivot_longer(cols = starts_with("Mean_AOI"), names_to = "AOI", values_to = "Duration_Percentage") %>%
  mutate(AOI = recode(AOI,
                      "Mean_AOI_Students_pct" = "Students",
                      "Mean_AOI_Disruptive_Person_pct" = "Disruptive Person",
                      "Mean_AOI_Teacher_Material_pct" = "Teacher Material",
                      "Mean_AOI_Student_Desk_pct" = "Student Desk",
                      "Mean_AOI_Classroom_Others_pct" = "Classroom/Others")) %>%
  arrange(Group, desc(Duration_Percentage))

# Step 6: Restructure data for grouping and calculate 95% CI for fixation durations
grouped_aoi_durations_ci <- aoi_durations_percentages %>%
  pivot_longer(
    cols = starts_with("AOI"),
    names_to = "AOI",
    values_to = "Duration_Percentage"
  ) %>%
  mutate(AOI = recode(
    AOI,
    "AOI_Students_pct" = "Students",
    "AOI_Disruptive_Person_pct" = "Disruptive Person",
    "AOI_Teacher_Material_pct" = "Teacher Material",
    "AOI_Student_Desk_pct" = "Student Desk",
    "AOI_Classroom_Others_pct" = "Classroom/Others"
  )) %>%
  group_by(Group, AOI) %>%
  summarise(
    Mean_Duration_Percentage = mean(Duration_Percentage, na.rm = TRUE),
    CI_Lower = Mean_Duration_Percentage - qt(0.975, df = n() - 1) * sd(Duration_Percentage, na.rm = TRUE) / sqrt(n()),
    CI_Upper = Mean_Duration_Percentage + qt(0.975, df = n() - 1) * sd(Duration_Percentage, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  )

# Map AOI names to clean versions for readability in the final results_duration table
results_duration$AOI <- recode(results_duration$AOI,
                      "AOI_Students" = "Students",
                      "AOI_Disruptive_Person" = "Disruptive Person",
                      "AOI_Teacher_Material" = "Teacher Material",
                      "AOI_Student_Desk" = "Student Desk",
                      "AOI_Classroom_Others" = "Classroom/Others")

#### Number of fixations per minute and fixation duration in ms (micro-teaching unit)
```{r nof_dur_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
##################### NUMBER OF FIXATIONS PER MINUTE ########################

##################### Data Preparation ########################
df_aoi_sum <- df_aoi %>%
  filter(TOI == "Lesson") %>%
  dplyr::select(
    Group,
    Participant,
    Duration_of_interval,
    starts_with("Total_duration_of_fixations"),
    starts_with("Number_of_fixations"),
    starts_with("Average_duration"),
    -contains("Disruptive_Person")
  ) %>%
  rowwise() %>%
  transmute(
    Group = factor(Group, levels = c("Expert", "Novice"), labels = c("Experienced", "Inexperienced")),
    Participant,
    Duration_of_interval_min = Duration_of_interval / 60000,
    Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
    Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
    Number_fixation_min_mtu = Sum_number_fixation / Duration_of_interval_min,
    Avg_fixation_duration = Sum_duration_fixation / Sum_number_fixation
  ) %>%
  drop_na()

# Descriptive Statistics for Number of Fixations per Minute
nof_stats <- df_aoi_sum %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    M = round(mean(Number_fixation_min_mtu, na.rm = TRUE), 2),
    SD = round(sd(Number_fixation_min_mtu, na.rm = TRUE), 2),
    Min = round(min(Number_fixation_min_mtu, na.rm = TRUE), 2),
    Max = round(max(Number_fixation_min_mtu, na.rm = TRUE), 2)
  )

# Display Table
knitr::kable(nof_stats, caption = "N, M, SD, Min & Max for Number of Fixations per Minute") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)

# t-Test and Cohen's d
t_test_mtu <- t.test(Number_fixation_min_mtu ~ Group, data = df_aoi_sum, var.equal = TRUE)
cohen_d_mtu <- cohen.d(Number_fixation_min_mtu ~ Group, data = df_aoi_sum)

# APA Table
t_test_result_mtu <- data.frame(
  "Group Comparison" = "Experienced vs. Inexperienced",
  "t-value" = round(t_test_mtu$statistic, 2),
  "df" = t_test_mtu$parameter,
  "p-value" = format.pval(t_test_mtu$p.value, digits = 2, eps = .05),
  "Mean Difference" = round(t_test_mtu$estimate[1] - t_test_mtu$estimate[2], 2),
  "Cohen's d" = round(cohen_d_mtu$estimate, 2),
  "95% CI (d)" = paste0("[", round(cohen_d_mtu$conf.int[1], 2), ", ", round(cohen_d_mtu$conf.int[2], 2), "]")
)

knitr::kable(t_test_result_mtu, caption = "t-Test and Effect Size for Number of Fixations per Minute") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)

# Ensure cohen_d_mtu is numeric
cohen_d_mtu <- round(as.numeric(cohen.d(Number_fixation_min_mtu ~ Group, data = df_aoi_sum)$estimate), 2)

# Plot: Number of Fixations per Minute
y_max_mtu <- max(df_aoi_sum$Number_fixation_min_mtu) * 1.5

plot_number_fixation_group <- df_aoi_sum %>%
  ggplot(aes(x = Group, y = Number_fixation_min_mtu, fill = Group)) +
  geom_boxplot(outlier.shape = 16, outlier.size = 2, width = 0.5) +
  geom_jitter(width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5) +
  stat_summary(fun = mean, geom = "point", shape = 4, size = 5, color = "blue", stroke = 1.2) +
  scale_fill_brewer(palette = "RdBu") +
  ylim(0, y_max_mtu) +
  labs(title = "Number of Fixations per Minute\n(Micro-Teaching Unit)", x = "", y = "Fixations per Minute") +
  theme_cowplot() +
  theme(legend.position = "none") +
  annotate("text", x = 1, y = 3,
           label = paste0("italic(M) == ", round(nof_stats$M[1], 2), " * ',' ~ italic(SD) == ", round(nof_stats$SD[1], 2)),
           hjust = 0.5, size = 4, parse = TRUE) +
  annotate("text", x = 2, y = 3,
           label = paste0("italic(M) == ", round(nof_stats$M[2], 2), " * ',' ~ italic(SD) == ", round(nof_stats$SD[2], 2)),
           hjust = 0.5, size = 4, parse = TRUE) +
  annotate("text", x = 1.5, y = y_max_mtu * 0.95,
           label = paste0("italic(p) == ", round(t_test_mtu$p.value, 2), " * ',' ~ italic(d) == ", cohen_d_mtu),
           hjust = 0.5, size = 4, fontface = "italic", parse = TRUE)

plot_number_fixation_group

ggsave(filename = "plots/plot_number_fixation_group.svg",
       width = 20,
       height = 12,
       units = "cm")

##################### Average Fixation Duration ########################

# Descriptive Statistics for Average Fixation Duration
fixation_stats <- df_aoi_sum %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    M = round(mean(Avg_fixation_duration, na.rm = TRUE), 2),
    SD = round(sd(Avg_fixation_duration, na.rm = TRUE), 2),
    Min = round(min(Avg_fixation_duration, na.rm = TRUE), 2),
    Max = round(max(Avg_fixation_duration, na.rm = TRUE), 2)
  )

# Display Table
knitr::kable(fixation_stats, caption = "N, M, SD, Min & Max for Average Fixation Duration") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)

# t-Test and Cohen's d
t_test_fixation <- t.test(Avg_fixation_duration ~ Group, data = df_aoi_sum, var.equal = TRUE)
cohen_d_fixation <- cohen.d(Avg_fixation_duration ~ Group, data = df_aoi_sum)

# APA Table
t_test_result_fixation <- data.frame(
  "Group Comparison" = "Experienced vs. Inexperienced",
  "t-value" = round(t_test_fixation$statistic, 2),
  "df" = t_test_fixation$parameter,
  "p-value" = format.pval(t_test_fixation$p.value, digits = 2, eps = .05),
  "Mean Difference" = round(t_test_fixation$estimate[1] - t_test_fixation$estimate[2], 2),
  "Cohen's d" = round(cohen_d_fixation$estimate, 2),
  "95% CI (d)" = paste0("[", round(cohen_d_fixation$conf.int[1], 2), ", ", round(cohen_d_fixation$conf.int[2], 2), "]")
)

knitr::kable(t_test_result_fixation, caption = "t-Test and Effect Size for Average Fixation Duration") %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = FALSE)

# Ensure cohen_d_fixation is numeric
cohen_d_fixation <- round(cohen.d(Avg_fixation_duration ~ Group, data = df_aoi_sum)$estimate, 2)

# Plot: Average Fixation Duration
plot_avg_fixation_group <- df_aoi_sum %>%
  ggplot(aes(x = Group, y = Avg_fixation_duration, fill = Group)) +
  geom_boxplot(outlier.shape = 16, outlier.size = 2, width = 0.5) +
  geom_jitter(width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5) +
  stat_summary(fun = mean, geom = "point", shape = 4, size = 5, color = "blue", stroke = 1.2) +
  scale_fill_brewer(palette = "RdBu") +
  labs(title = "Average Fixation Duration\n(Micro-Teaching Unit)", x = "", y = "Fixation Duration (ms)") +
  theme_cowplot() +
  theme(legend.position = "none") +
  # Add M and SD values below the x-axis for each group
  annotate("text", x = 1, y = -50,  # Adjust y-coordinate to place below the x-axis
           label = paste0("italic(M) == ", round(fixation_stats$M[1], 2), " * ',' ~ italic(SD) == ", round(fixation_stats$SD[1], 2)),
           hjust = 0.5, size = 4, parse = TRUE) +
  annotate("text", x = 2, y = -50,  # Adjust y-coordinate to place below the x-axis
           label = paste0("italic(M) == ", round(fixation_stats$M[2], 2), " * ',' ~ italic(SD) == ", round(fixation_stats$SD[2], 2)),
           hjust = 0.5, size = 4, parse = TRUE) +
  # Add p-value and d-value above the plot
  annotate("text", x = 1.5, y = max(df_aoi_sum$Avg_fixation_duration) * 1.1,
           label = paste0("italic(p) == ", round(t_test_fixation$p.value, 2), " * ',' ~ italic(d) == ", cohen_d_fixation),
           hjust = 0.5, size = 4, fontface = "italic", parse = TRUE)

plot_avg_fixation_group

ggsave(filename = "plots/plot_avg_fixation_group.svg",
       width = 20,
       height = 12,
       units = "cm")

# Load the patchwork library
install.packages("patchwork")
library(patchwork)

# Combine the two plots side by side
combined_plot <- plot_number_fixation_group + plot_avg_fixation_group +
  plot_layout(ncol = 2, guides = "collect") &
  theme(legend.position = "none")

# Display the combined plot
combined_plot

# Save the combined plot
ggsave(
  filename = "plots/combined_results_plot.svg",
  plot = combined_plot,
  width = 25,
  height = 12,
  units = "cm"
)

@@

##################### SECOND PLOT: NUMBER OF FIXATIONS BY CATEGORY (AOI DISRUPTIVE PERSON) ########################

>>>>

# Gaze Behavior Across Areas of Interest 
```{r nof__dur_percent, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#### Percentage of fixation durations on each AOI, relative to the total duration of fixations during the entire "Lesson" 
# Step 1: Define AOI categories with correct column names for fixation duration
aoi_columns <- list(
  "AOI_Students" = c(
    "Total_duration_of_fixations.Anna",
    "Total_duration_of_fixations.Bianca",
    "Total_duration_of_fixations.Carl(a)"
  ),
  "AOI_Disruptive_Person" = c("Total_duration_of_fixations.Disruptive_Person"),
  "AOI_Teacher_Material" = c(
    "Total_duration_of_fixations.Board_Screen",
    "Total_duration_of_fixations.Material_Teacher"
  ),
  "AOI_Student_Desk" = c(
    "Total_duration_of_fixations.Nametag_Anna",
    "Total_duration_of_fixations.Nametag_Bianca",
    "Total_duration_of_fixations.Nametag_Carl(a)",
    "Total_duration_of_fixations.Material_Students"
  ),
  "AOI_Classroom_Others" = c("Total_duration_of_fixations.Classroom_Others")
)

# Step 3: Calculate total fixation duration per participant, excluding "Disruptive Student"
relevant_columns <- unlist(aoi_columns[c("AOI_Students", "AOI_Teacher_Material", "AOI_Student_Desk", "AOI_Classroom_Others")])

# Step 5: Summarize fixation duration percentages by Group and arrange in descending order
grouped_aoi_durations_percentages <- aoi_durations_percentages %>%
  group_by(Group) %>%
  summarise(
    Mean_AOI_Students_pct = round(mean(AOI_Students_pct, na.rm = TRUE), 2),
    Mean_AOI_Disruptive_Person_pct = round(mean(AOI_Disruptive_Person_pct, na.rm = TRUE), 2),
    Mean_AOI_Teacher_Material_pct = round(mean(AOI_Teacher_Material_pct, na.rm = TRUE), 2),
    Mean_AOI_Student_Desk_pct = round(mean(AOI_Student_Desk_pct, na.rm = TRUE), 2),
    Mean_AOI_Classroom_Others_pct = round(mean(AOI_Classroom_Others_pct, na.rm = TRUE), 2)
  ) %>%
  pivot_longer(cols = starts_with("Mean_AOI"), names_to = "AOI", values_to = "Duration_Percentage") %>%
  mutate(AOI = recode(AOI,
                      "Mean_AOI_Students_pct" = "Students",
                      "Mean_AOI_Disruptive_Person_pct" = "Disruptive Student",
                      "Mean_AOI_Teacher_Material_pct" = "Teacher Material",
                      "Mean_AOI_Student_Desk_pct" = "Student Desk",
                      "Mean_AOI_Classroom_Others_pct" = "Classroom/Others")) %>%
  arrange(Group, desc(Duration_Percentage))

# Step 6: Restructure data for grouping and calculate 95% CI for fixation durations
grouped_aoi_durations_ci <- aoi_durations_percentages %>%
  pivot_longer(
    cols = starts_with("AOI"),
    names_to = "AOI",
    values_to = "Duration_Percentage"
  ) %>%
  mutate(AOI = recode(
    AOI,
    "AOI_Students_pct" = "Students",
    "AOI_Disruptive_Person_pct" = "Disruptive Student",
    "AOI_Teacher_Material_pct" = "Teacher Material",
    "AOI_Student_Desk_pct" = "Student Desk",
    "AOI_Classroom_Others_pct" = "Classroom/Others"
  )) %>%
  group_by(Group, AOI) %>%
  summarise(
    Mean_Duration_Percentage = mean(Duration_Percentage, na.rm = TRUE),
    CI_Lower = Mean_Duration_Percentage - qt(0.975, df = n() - 1) * sd(Duration_Percentage, na.rm = TRUE) / sqrt(n()),
    CI_Upper = Mean_Duration_Percentage + qt(0.975, df = n() - 1) * sd(Duration_Percentage, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  )

# Map AOI names to clean versions for readability in the final results_duration table
results_duration$AOI <- recode(results_duration$AOI,
                      "AOI_Students" = "Students",
                      "AOI_Disruptive_Person" = "Disruptive Student",
                      "AOI_Teacher_Material" = "Teacher Material",
                      "AOI_Student_Desk" = "Student Desk",
                      "AOI_Classroom_Others" = "Classroom/Others")

#### Percentage of fixations on each AOI, relative to the total number of fixations during the entire "Lesson" 
# Step 1: Define AOI categories
aoi_columns <- list(
  "AOI_Students" = c(
    "Number_of_fixations.Anna",
    "Number_of_fixations.Bianca",
    "Number_of_fixations.Carl(a)"
  ),
  "AOI_Disruptive_Person" = c("Number_of_fixations.Disruptive_Person"),
  "AOI_Teacher_Material" = c(
    "Number_of_fixations.Board_Screen",
    "Number_of_fixations.Material_Teacher"
  ),
  "AOI_Student_Desk" = c(
    "Number_of_fixations.Nametag_Anna",
    "Number_of_fixations.Nametag_Bianca",
    "Number_of_fixations.Nametag_Carl(a)",
    "Number_of_fixations.Material_Students"
  ),
  "AOI_Classroom_Others" = c("Number_of_fixations.Classroom_Others")
)

@@

# Step 3: Calculate total fixations per participant, excluding "Disruptive Student"
# Extract relevant column names excluding "Disruptive Student"
relevant_columns <- unlist(aoi_columns[c("AOI_Students", "AOI_Teacher_Material", "AOI_Student_Desk", "AOI_Classroom_Others")])

@@

# Step 5: Summarize fixation percentages by Group and arrange in descending order
grouped_aoi_percentages <- aoi_percentages %>%
  group_by(Group) %>%
  summarise(
    Mean_AOI_Students_pct = round(mean(AOI_Students_pct, na.rm = TRUE), 2),
    Mean_AOI_Disruptive_Person_pct = round(mean(AOI_Disruptive_Person_pct, na.rm = TRUE), 2),
    Mean_AOI_Teacher_Material_pct = round(mean(AOI_Teacher_Material_pct, na.rm = TRUE), 2),
    Mean_AOI_Student_Desk_pct = round(mean(AOI_Student_Desk_pct, na.rm = TRUE), 2),
    Mean_AOI_Classroom_Others_pct = round(mean(AOI_Classroom_Others_pct, na.rm = TRUE), 2)
  ) %>%
  pivot_longer(cols = starts_with("Mean_AOI"), names_to = "AOI", values_to = "Fixation_Percentage") %>%
  mutate(AOI = recode(AOI,
                      "Mean_AOI_Students_pct" = "Students",
                      "Mean_AOI_Disruptive_Person_pct" = "Disruptive Student",
                      "Mean_AOI_Teacher_Material_pct" = "Teacher Material",
                      "Mean_AOI_Student_Desk_pct" = "Student Desk",
                      "Mean_AOI_Classroom_Others_pct" = "Classroom/Others")) %>%
  arrange(Group, desc(Fixation_Percentage))

# Step 6: Restructure data for grouping and calculate 95% CI
grouped_aoi_percentages_ci <- aoi_percentages %>%
  pivot_longer(
    cols = starts_with("AOI"),
    names_to = "AOI",
    values_to = "Percentage"
  ) %>%
  mutate(AOI = recode(
    AOI,
    "AOI_Students_pct" = "Students",
    "AOI_Disruptive_Person_pct" = "Disruptive Student",
    "AOI_Teacher_Material_pct" = "Teacher Material",
    "AOI_Student_Desk_pct" = "Student Desk",
    "AOI_Classroom_Others_pct" = "Classroom/Others"
  )) %>%
  group_by(Group, AOI) %>%
  summarise(
    Mean_Percentage = mean(Percentage, na.rm = TRUE),
    CI_Lower = Mean_Percentage - qt(0.975, df = n() - 1) * sd(Percentage, na.rm = TRUE) / sqrt(n()),
    CI_Upper = Mean_Percentage + qt(0.975, df = n() - 1) * sd(Percentage, na.rm = TRUE) / sqrt(n()),
    .groups = "drop"
  )

@@

# Clean up AOI names for readability in the final table
aoi_name_mapping <- c(
  "AOI_Students" = "Students",
  "AOI_Disruptive_Person" = "Disruptive Student",
  "AOI_Teacher_Material" = "Teacher Material",
  "AOI_Student_Desk" = "Student Desk",
  "AOI_Classroom_Others" = "Classroom/Others"
)
results_number$AOI <- aoi_name_mapping[results_number$AOI]

@@

#### Number of fixations per minute and fixation duration in ms (micro-teaching unit)
```{r nof_dur_all, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# ##################### NUMBER OF FIXATIONS PER MINUTE ########################
# ##################### Data Preparation ########################
# df_aoi_sum <- df_aoi %>%
#   filter(TOI == "Lesson") %>%
#   dplyr::select(
#     Group,
#     Participant,
#     Duration_of_interval,
#     starts_with("Total_duration_of_fixations"),
#     starts_with("Number_of_fixations"),
#     starts_with("Average_duration"),
#     -contains("Disruptive_Person")
#   rowwise() %>%
#   transmute(
#     Group = factor(Group, levels = c("Expert", "Novice"), labels = c("Experienced", "Inexperienced")),
#     Participant,
#     Duration_of_interval_min = Duration_of_interval / 60000,
#     Sum_duration_fixation = sum(c_across(starts_with("Total_duration")), na.rm = TRUE),
#     Sum_number_fixation = sum(c_across(starts_with("Number_of")), na.rm = TRUE),
#     Number_fixation_min_mtu = Sum_number_fixation / Duration_of_interval_min,
#     Avg_fixation_duration = Sum_duration_fixation / Sum_number_fixation
# ##################### Number of Fixations per Minute ########################
# # Descriptive Statistics for Number of Fixations per Minute
# nof_stats <- df_aoi_sum %>%
#     M = round(mean(Number_fixation_min_mtu, na.rm = TRUE), 2),
#     SD = round(sd(Number_fixation_min_mtu, na.rm = TRUE), 2),
#     Min = round(min(Number_fixation_min_mtu, na.rm = TRUE), 2),
#     Max = round(max(Number_fixation_min_mtu, na.rm = TRUE), 2)
# # Display Table
# knitr::kable(nof_stats, caption = "N, M, SD, Min & Max for Number of Fixations per Minute") %>%
# # t-Test and Cohen's d
# t_test_mtu <- t.test(Number_fixation_min_mtu ~ Group, data = df_aoi_sum, var.equal = TRUE)
# cohen_d_mtu <- cohen.d(Number_fixation_min_mtu ~ Group, data = df_aoi_sum)
# # APA Table
# t_test_result_mtu <- data.frame(
#   "Group Comparison" = "Experienced vs. Inexperienced",
#   "t-value" = round(t_test_mtu$statistic, 2),
#   "df" = t_test_mtu$parameter,
#   "p-value" = format.pval(t_test_mtu$p.value, digits = 2, eps = .05),
#   "Mean Difference" = round(t_test_mtu$estimate[1] - t_test_mtu$estimate[2], 2),
#   "Cohen's d" = round(cohen_d_mtu$estimate, 2),
#   "95% CI (d)" = paste0("[", round(cohen_d_mtu$conf.int[1], 2), ", ", round(cohen_d_mtu$conf.int[2], 2), "]")
# knitr::kable(t_test_result_mtu, caption = "t-Test and Effect Size for Number of Fixations per Minute") %>%
# # Ensure cohen_d_mtu is numeric
# cohen_d_mtu <- round(as.numeric(cohen.d(Number_fixation_min_mtu ~ Group, data = df_aoi_sum)$estimate), 2)
# # Plot: Number of Fixations per Minute
# y_max_mtu <- max(df_aoi_sum$Number_fixation_min_mtu) * 1.5
# plot_number_fixation_group <- df_aoi_sum %>%
#   ggplot(aes(x = Group, y = Number_fixation_min_mtu, fill = Group)) +
#   geom_boxplot(outlier.shape = 16, outlier.size = 2, width = 0.5) +
#   geom_jitter(width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5) +
#   stat_summary(fun = mean, geom = "point", shape = 4, size = 5, color = "blue", stroke = 1.2) +
#   ylim(0, y_max_mtu) +
#   labs(title = "Number of Fixations per Minute\n(Micro-Teaching Unit)", x = "", y = "Fixations per Minute") +
#   annotate("text", x = 1, y = 3,
#            label = paste0("italic(M) == ", round(nof_stats$M[1], 2), " * ',' ~ italic(SD) == ", round(nof_stats$SD[1], 2)),
#            hjust = 0.5, size = 4, parse = TRUE) +
#   annotate("text", x = 2, y = 3,
#            label = paste0("italic(M) == ", round(nof_stats$M[2], 2), " * ',' ~ italic(SD) == ", round(nof_stats$SD[2], 2)),
#            hjust = 0.5, size = 4, parse = TRUE) +
#   annotate("text", x = 1.5, y = y_max_mtu * 0.95,
#            label = paste0("italic(p) == ", round(t_test_mtu$p.value, 2), " * ',' ~ italic(d) == ", cohen_d_mtu),
#            hjust = 0.5, size = 4, fontface = "italic", parse = TRUE)
# plot_number_fixation_group
# ggsave(filename = "plots/plot_number_fixation_group.svg",
# ##################### Average Fixation Duration ########################
# # Descriptive Statistics for Average Fixation Duration
# fixation_stats <- df_aoi_sum %>%
#     M = round(mean(Avg_fixation_duration, na.rm = TRUE), 2),
#     SD = round(sd(Avg_fixation_duration, na.rm = TRUE), 2),
#     Min = round(min(Avg_fixation_duration, na.rm = TRUE), 2),
#     Max = round(max(Avg_fixation_duration, na.rm = TRUE), 2)
# # Display Table
# knitr::kable(fixation_stats, caption = "N, M, SD, Min & Max for Average Fixation Duration") %>%
# # t-Test and Cohen's d
# t_test_fixation <- t.test(Avg_fixation_duration ~ Group, data = df_aoi_sum, var.equal = TRUE)
# cohen_d_fixation <- cohen.d(Avg_fixation_duration ~ Group, data = df_aoi_sum)
# # APA Table
# t_test_result_fixation <- data.frame(
#   "Group Comparison" = "Experienced vs. Inexperienced",
#   "t-value" = round(t_test_fixation$statistic, 2),
#   "df" = t_test_fixation$parameter,
#   "p-value" = format.pval(t_test_fixation$p.value, digits = 2, eps = .05),
#   "Mean Difference" = round(t_test_fixation$estimate[1] - t_test_fixation$estimate[2], 2),
#   "Cohen's d" = round(cohen_d_fixation$estimate, 2),
#   "95% CI (d)" = paste0("[", round(cohen_d_fixation$conf.int[1], 2), ", ", round(cohen_d_fixation$conf.int[2], 2), "]")
# knitr::kable(t_test_result_fixation, caption = "t-Test and Effect Size for Average Fixation Duration") %>%
# # Ensure cohen_d_fixation is numeric
# cohen_d_fixation <- round(cohen.d(Avg_fixation_duration ~ Group, data = df_aoi_sum)$estimate, 2)
# # Plot: Average Fixation Duration
# plot_avg_fixation_group <- df_aoi_sum %>%
#   ggplot(aes(x = Group, y = Avg_fixation_duration, fill = Group)) +
#   geom_boxplot(outlier.shape = 16, outlier.size = 2, width = 0.5) +
#   geom_jitter(width = 0.15, height = 0.1, alpha = 0.5, color = "black", size = 1.5) +
#   stat_summary(fun = mean, geom = "point", shape = 4, size = 5, color = "blue", stroke = 1.2) +
#   labs(title = "Average Fixation Duration\n(Micro-Teaching Unit)", x = "", y = "Fixation Duration (ms)") +
#   # Add M and SD values below the x-axis for each group
#   annotate("text", x = 1, y = -50,  # Adjust y-coordinate to place below the x-axis
#            label = paste0("italic(M) == ", round(fixation_stats$M[1], 2), " * ',' ~ italic(SD) == ", round(fixation_stats$SD[1], 2)),
#            hjust = 0.5, size = 4, parse = TRUE) +
#   annotate("text", x = 2, y = -50,  # Adjust y-coordinate to place below the x-axis
#            label = paste0("italic(M) == ", round(fixation_stats$M[2], 2), " * ',' ~ italic(SD) == ", round(fixation_stats$SD[2], 2)),
#            hjust = 0.5, size = 4, parse = TRUE) +
#   # Add p-value and d-value above the plot
#   annotate("text", x = 1.5, y = max(df_aoi_sum$Avg_fixation_duration) * 1.1,
#            label = paste0("italic(p) == ", round(t_test_fixation$p.value, 2), " * ',' ~ italic(d) == ", cohen_d_fixation),
#            hjust = 0.5, size = 4, fontface = "italic", parse = TRUE)
# plot_avg_fixation_group
# ggsave(filename = "plots/plot_avg_fixation_group.svg",
# # Load the patchwork library
# install.packages("patchwork")
# library(patchwork)
# # Combine the two plots side by side
# combined_plot <- plot_number_fixation_group + plot_avg_fixation_group +
#   plot_layout(ncol = 2, guides = "collect") &
# # Display the combined plot
# combined_plot
# # Save the combined plot
# ggsave(
#   filename = "plots/combined_results_plot.svg",
#   plot = combined_plot,
#   width = 25,
#   units = "cm"

@@

##################### SECOND PLOT: NUMBER OF FIXATIONS BY CATEGORY (AOI Disruptive Student) ########################
